Black swans in ecological time series\\Black swans in population dynamics\\Heavy tailed ecological time series

### 2014-09-25 anderson-etal-blackswan-timeseries.tex
Touch up fig 2

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{nu-covariates-base.pdf}
\includegraphics[width=0.7\textwidth]{brook-etal-correlates.pdf}
\caption{
  (\textit{To be redone with 6 panels: 3 parameters, data point number, log length, minimum age or lifespan.})
  A number of hypotheses for what could be driving $\nu$ values. From top left to bottom right: $\phi$ (AR1 coefficient), $\log \sigma_\mathrm{proc}$ (log process error standard deviation), $N$ (time series length), $b$ (density dependence parameter in the Gompertz model; 1 is density independent and 0 is maximally density dependent), $\lambda$ (growth parameter from Gompertz model).  
  All dots show median estimates and vertical line segments show 50\% credible intervals of posterior for the $\nu$ values.}
\label{fig:correlates}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{nu-covariates-base.pdf}
\includegraphics[width=0.7\textwidth]{brook-etal-correlates.pdf}
\caption{
  (\textit{\textbf{To be redone with 6 panels: 3 parameters, data point number, log length, minimum age or lifespan.}})
  A number of hypotheses for what could be driving $\nu$ values. From top left to bottom right: $\phi$ (AR1 coefficient), $\log \sigma_\mathrm{proc}$ (log process error standard deviation), $N$ (time series length), $b$ (density dependence parameter in the Gompertz model; 1 is density independent and 0 is maximally density dependent), $\lambda$ (growth parameter from Gompertz model).  
  All dots show median estimates and vertical line segments show 50\% credible intervals of posterior for the $\nu$ values.}
\label{fig:correlates}
\end{center}
\end{figure}
